### 2018-03-23 Maths Notes/Further Pure/FP2/Maclaurin and Taylor Series/Maclaurin and Taylor Series.tex
Notes up to date

\begin{document}
\begin{center}
\underline{\huge Maclaurin and Taylor Series}
\end{center}
\section{Maclaurin's expansion}
$$f(x)=f(0)+f'(0)x+f''(0)\frac{x^2}{2!}+f'''(0)\frac{x^3}{3!}+...+f^r(0)\frac{x^r}{r!}...$$
\\
For the continuous function, f, given by $f:x\Rightarrow f(x)$(where $x$ is real), then providing $f(0),f'(0),f''(0)$ etc all have finite values. This is an infinite series.
\subsection{Example}
\textit{Given that $f(x)=e^x$ can be written as an infinite series in the form:}
$$f(x)=e^x=a_0+a_1x+a_2x^2+a_3x^3+...+a_rx^4+...$$
\textit{And that it is valid to differentiate an infinite series term by term, show that:}
$$e^2=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
\\
\\
\textcolor{red}{Find up to the third differential of $f(x)$ and the value of zero for each}\\
\begin{tabular}{l l}
$f(x)=e^x$&$f(0)=1$\\
$f'(x)=e^x$&$f''(0)=1$\\
$f''(x)=e^x$&$f''(0)=1$\\
$f'''(x)=e^x$&$f'''(0)=1$
\end{tabular}
\\
\\
$$f(x)=1+1\times x+1\times\frac{x^2}{2!}+1\times\frac{x^3}{3!}$$
$$f(x)=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
\subsection{Standard results}
Standard results are given on the data sheet, these can then be used for adapted forms of the results also. Remember to consider the limits where appropriate.

\end{document}

>>>>

\begin{document}
\begin{center}
\underline{\huge Maclaurin and Taylor Series}
\end{center}
\section{Maclaurin's expansion}
$$f(x)=f(0)+f'(0)x+f''(0)\frac{x^2}{2!}+f'''(0)\frac{x^3}{3!}+...+f^r(0)\frac{x^r}{r!}...$$
\\
For the continuous function, f, given by $f:x\Rightarrow f(x)$(where $x$ is real), then providing $f(0),f'(0),f''(0)$ etc all have finite values. This is an infinite series.
\subsection{Example}
\textit{Given that $f(x)=e^x$ can be written as an infinite series in the form:}
$$f(x)=e^x=a_0+a_1x+a_2x^2+a_3x^3+...+a_rx^4+...$$
\textit{And that it is valid to differentiate an infinite series term by term, show that:}
$$e^2=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
\\
\\
\textcolor{red}{Find up to the third differential of $f(x)$ and the value of zero for each}\\
\begin{tabular}{l l}
$f(x)=e^x$&$f(0)=1$\\
$f'(x)=e^x$&$f''(0)=1$\\
$f''(x)=e^x$&$f''(0)=1$\\
$f'''(x)=e^x$&$f'''(0)=1$
\end{tabular}
\\
\\
$$f(x)=1+1\times x+1\times\frac{x^2}{2!}+1\times\frac{x^3}{3!}$$
$$f(x)=1+x+\frac{x^2}{2!}+\frac{x^3}{3!}+...+\frac{x^r}{r!}+...$$
\subsection{Standard results}
Standard results are given on the data sheet, these can then be used for adapted forms of the results also. Remember to consider the limits where appropriate.
\newpage
\section{Taylor expansion}
The conditions of the Maclaurin expansion mean that some functions, such as $\ln x$ cannot be expanded as a series in ascending powers of x.\\
\\
The construction of the Maclaurin expansion focuses on $x=0$ and values of x very close to zero. The Taylor expansion focuses on $x=a$.\\
\\
Considering the functions f and g, where $f(x+a)\equiv g(x)$ then:\\
$f^r(a)=g^r(0)$\\
\\
Turning the Maclaurin expansion for g from:
$$g(x)=g(0)+g'(0)x+\frac{g''(0)}{2!}x^2...$$
Into
$$f(x+a)=f(a)+f'(a)x+\frac{f''(a)}{2!}x^2+...+\frac{f^r(a)}{r!}x^r$$
Replacing x by x-a gives
$$f(x)=f(a)+f'(a)(x-a)+\frac{f''(a)}{2!}(x-a)^2+...+\frac{f^r(a)}{r!}(x-a)^r$$
These are the two forms of the Taylor expansion, when a=0, they both become the Maclaurin expansion.
\end{document}

### 2018-03-23 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
Notes up to date

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

@@

@@

\end{document}

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{enumitem}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty=10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S3}
\rfoot{Page \thepage}

@@

\section{Goodness of fit}

@@

\section{Contingency tables}
\item We use this test to see if two factors are independent of each other
\item We describe them by: Number of rows $\times$ Number of columns
\item $H_0$ is that they are independent
\item $H_1$ is that they are independent
\item $$\textrm{Expected values}=\frac{\textrm{Row total}\times\textrm{Column total}}{\textrm{Grand total}}$$
\item $$\nu=(\textrm{Number of rows-1})(\textrm{Number of columns-1})$$
\subsection{Contingency tables}
\textit{Determine to the 5\% significance level whether school and grade are dependent}\\

\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
&&\multicolumn{3}{|X|}{Grade}&\multirow{2}{4em}{Totals}\\
\cline{3-5}
&&A&B&C&\\
\hline
\multirow{2}{4em}{School}&X&18&12&20&50\\
\cline{2-6}
&Y&26&12&32&70\\
\hline
Totals&&44&24&52&120\\
\hline
\end{tabularx}
\\
\\
\textcolor{red}{Write the hypotheses}
\begin{center}
$H_0:$ School and grade are independent\\
$H_1:$ School and grade are not independent\\
\end{center}
\textcolor{red}{Calculate the expected frequencies, using the formula to find expected values}\\

\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
&&\multicolumn{3}{|X|}{Grade}\\
\hline
&&A&B&C\\
\hline
\multirow{2}{4em}{School}&X&$$\frac{55}{3}$$&$$10$$&$$\frac{65}{3}$$\\
\cline{2-5}
&Y&$$\frac{77}{3}$$&$$14$$&$$\frac{91}{3}$$\\
\hline
\end{tabularx}
\textcolor{red}{Calculate the degrees of freedom}
$$\nu=(2-1)(3-1)=2$$
\textcolor{red}{Calculate $X^2$}
$$X^2=0.916$$
\textcolor{red}{Find the value of $\chi^2_2$ at 5\%}
$$\chi^2_2=5.991$$
\textcolor{red}{Compare values and write conclusion}
\begin{center}
$0.916<5.991$ don't reject $H_0$, insufficient evidence to suggest an association, independent
\end{center}
\end{document}
